Turbulence in compact to giant HII regions

### 2022-01-21 strucfunc_paper.tex
Figure caption for histograms

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/Hist}\par
 \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
 \label{fig:hist}
\end{figure*}

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/Hist}\par
 \caption{
   Histograms of the plane-of-sky variation in the \ha{} centroid velocities.
   Each panel shows the fraction of the observed spatial points
   (pixels or fiber positions)
   with a given velocity offset from the mean systemic velocity of each region.
   The RMS width \(\sigma\pos\) of each distribution is marked,
   as is the number of spatial points.
   The bin width is \SI{1}{km.s^{-1}} and the regions are arranged
   in order of decreasing \(\sigma\pos\).
 }
 \label{fig:hist}
\end{figure*}
